%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Matthew Bonsall} % Your name
\address{787 The Alameda Apt 204 \\ San Jose, CA 95126} % Your address
\address{(678)-908-1996 \\ MVB0005@Auburn.edu \\ GitHub.com/MVB0005} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Auburn University, Auburn, AL} \hfill {\em Graduation: May 2018} \\ 
B.E. in Software Engineering \\
Academic Common Market Scholarship (2016 - Graduation) \\
Academic Founders Scholarship (2014 - Graduation)\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Vertafore, Inc}{November 2018 - May 2019}{Software Engineer 2}{Denver, CO}
\item Mentored Team on Best Practices and Difficult Coding Problems.
\item Participated in Code Review Process as both Reviewer and Reviewee. 
\item Designed and Built Integrations between Enterprise Products.
\item Created Automation Tools that Saved Developers Hundreds of Hours of Work. 
\item Led Team to Victory over 20 teams in Corporate Hackathon by Completing an Enormous Project in just 18 hours.
\end{rSubsection}

\begin{rSubsection}{Vertafore, Inc}{July 2018 - November 2018}{Software Engineer 1}{Denver, CO}
\item Promoted in Record Time after demonstrating Technical and Leadership abilities.
\item Worked as a member of an Agile Scrum Team to define Technical Solutions that meet Business Requirements. 
\item Designed, Developed, Tested, and Debugged Heavily Trafficked Enterprise Applications. 
\item Successfully Demonstrated a Strategy to Migrate Legacy Software to AWS and Azure. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Auburn University}{September 2017 - May 2018}{Research Assistant for Dr. Gerry Dozier}{Auburn, AL}
\item Created a General Regression Neural Network that could Determine Authors and Recipients given a Collection of Correspondence.
\item Used Python to develop Feature Vectors from text correspondence.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Auburn Facilities Management}{January 2018 - May 2018}{Software Programmer}{Auburn, AL}
\item Created a Web Application and Adobe Navisworks plugin to allow users to easily Create, Read, Modify, and Delete Safety Information for Facilities.
\item The Navisworks plugin used C\# to make calls to our RESTful API using JSON.
\item Made Heavy Use of JavaScript and Python Flask in Application and API Development.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C\#, Python, JavaScript, Java \\
Protocols \& APIs & GIT, JSON, RESTful, XML \\
Databases & MySQL, MongoDB, ElasticSearch \\
Tools & Kibana, LaTeX, AWS, Azure, Postman, Fiddler
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
